---
title: "Homework 7"
author: "Jeff Nguyen"
date: "09/12/2020"
output:
  pdf_document:
    extra_dependencies: ["dsfont"]
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, envir=.GlobalEnv)
```

**Pre-MFE Probability Seminar**  
**Baruch College, Fall 2020**  


Homework 07  
Student Name: Ngoc Son (Jeff) Nguyen  


# **Question 1**  

Consider the random variable $X_1, X_2, ..., X_{10000}$ as the annual payout to customer's insurance claim.  

We are given $E[X_i] = \mu = 10^3$ and $Var[X_i] = 8*10^2$.  

We are looking to find the average charge to each customer denoting $\Pi$ so that the probability of the event that the sum of annual payout to each customer not exceeding the total annual charge for each customer is exactly $99.5\%$, i.e.:  

\begin{equation}
  \begin{aligned}
    \mathds{P}\Big[ X_1 + ... + X_{10000} \leqslant 10^4\Pi \Big] =& .995 \\
    \mathds{P}\Big[ X_1 + ... + X_{10000} - 10^4\mu \leqslant 10^4\Pi - 10^4\mu \Big] =& .995 \\
    \mathds{P}\Big[ \frac{X_1 + ... + X_{10000} - 10^4*10^3}{\sqrt{10^4}\sqrt{8*10^2}} \leqslant \frac{10^4\Pi - 10^4*10^3}{\sqrt{10^4}\sqrt{8*10^2}} \Big] =& .995 \\
    \mathds{P}\Big[ \frac{X_1 + ... + X_{10000} - 10^4*10^3}{10^3*2\sqrt{2}} \leqslant \frac{10^4(\Pi -10^3)}{10^3*2\sqrt{2}} \Big] =& .995 \\
    \mathds{P}\Big[ \frac{X_1 + ... + X_{10000} - 10^4*10^3}{10^3*2\sqrt{2}} \leqslant \frac{5(\Pi -10^3)}{\sqrt{2}} \Big] =& .995 \\
    N\Big[ \frac{5(\Pi -10^3)}{\sqrt{2}} \Big] =& .995  \quad \text{(Central Limit Theorem)}  \\
    \frac{1}{\sqrt{2\pi}} \int_{-\infty}^{\frac{5(\Pi -10^3)}{\sqrt{2}}} e^{-\frac{t^2}{2}}dt =& .995  \\
    \frac{1}{\sqrt{2\pi}} \frac{\sqrt{\pi}}{\sqrt{2}}erf\Big( \frac{t}{\sqrt{2}} \Big) \Big|_{t=-\infty}^{t={\frac{5(\Pi -10^3)}{\sqrt{2}}}} =& .995  \\
    \frac{1}{2}erf\Big[ \frac{5(\Pi -10^3)}{2} \Big] + \frac{1}{2} =& .995  \\
    erf\Big[ \frac{5(\Pi -10^3)}{2} \Big] =& .99  \\
    \frac{5(\Pi -10^3)}{2} =& erf^{-1}(.99)  \\
    \Pi =& \frac{2erf^{-1}(.99) + 10^3}{5}  \\
  \end{aligned}
\end{equation}

```{r}
erf.inv <- function(x) qnorm((x + 1)/2)/sqrt(2)  # inverse erf function
Pi <- (2*erf.inv(.99)+10^3)/5
```

Using R to approximate, we have the necessary average annual charge to each customer to be $\Pi = \frac{2erf^{-1}(.99) + 10^3}{5} \approx `r Pi`$, or approximately $\$ `r round(Pi,2)`$.  

# **Question 2**  

X, Y are bivariate normal random variables, following $X \sim N(\mu_X, \sigma_X^2)$, $Y \sim N(\mu_Y, \sigma_Y^2)$ and $\rho(X,Y) = \rho$.  


By definition, their joint pdf is given by:  

\begin{equation}
  \begin{aligned}
    f_{XY} = \frac{1}{2 \pi \sigma_X \sigma_Y \sqrt{1-\rho^2}} * e^{-{\frac{1}{2(1-\rho^2)}}*{\Big[ \Big( \frac{x-\mu_X}{\sigma_X} \Big)^2 + \Big( \frac{y-\mu_Y}{\sigma_Y} \Big)^2 - 2\rho\frac{(x-\mu_X)(y-\mu_Y)}{\sigma_X\sigma_Y}  \Big]}}
  \end{aligned}
\end{equation}
  
There exists $Z_1$ and $Z_2$ random variable such that $Z_1 \sim N(0,1)$ and $Z_2 \sim N(0,1)$ such that:

\begin{equation}
  \begin{aligned}
    \left\{
      \begin{matrix}
        X =& \sigma_X(\rho Z_1 + \sqrt{1 - \rho^2}Z_2) + \mu_X  \\
        Y =& \sigma_Y Z_1 + \mu_Y  \\
      \end{matrix}
    \right.
  \end{aligned}
\end{equation}

Thus, given $Y=y$, we have:  

\begin{equation}
  \begin{aligned}
    y =& \sigma_Y Z_1 + \mu_Y  \\
    Z_1 =& \frac{y - \mu_Y}{\sigma_Y}
  \end{aligned}
\end{equation}

In addition:

\begin{equation}
  \begin{aligned}
    X =& \sigma_X(\rho Z_1 + \sqrt{1 - \rho^2}Z_2) + \mu_X  \\
      =& \sigma_X(\rho \frac{y - \mu_Y}{\sigma_Y} + \sqrt{1 - \rho^2}Z_2) + \mu_X  \\
      =& \sigma_X \rho \frac{y - \mu_Y}{\sigma_Y} + \sigma_X \sqrt{1 - \rho^2}Z_2 + \mu_X  \\
  \end{aligned}
\end{equation}

Since $Z_1$ and $Z_2$ are independent, given $Y=y$, we can see $X$ is a linear function of $Z_2$, thus:

\begin{equation}
  \begin{aligned}
    \mathds{E}[X \Big| Y=y] =& \mathds{E} \Big[ {\sigma_X \rho \frac{y - \mu_Y}{\sigma_Y} + \sigma_X \sqrt{1 - \rho^2}Z_2 + \mu_X} \Big| Y=y \Big]  \\
                      =& \mathds{E} \Big[ \sigma_X \rho \frac{y - \mu_Y}{\sigma_Y} \Big| Y=y \Big] + \mathds{E} \Big[ \sigma_X \sqrt{1 - \rho^2}Z_2 \Big| Y=y \Big] + \mathds{E} [\mu_X \Big| Y=y ]  \\
                      =& \sigma_X \rho \frac{y - \mu_Y}{\sigma_Y} + \sigma_X \sqrt{1 - \rho^2} \mathds{E}[Z_2] + \mu_X  \\
                      =& \sigma_X \rho \frac{y - \mu_Y}{\sigma_Y} + \sigma_X \sqrt{1 - \rho^2} * 0 + \mu_X  \\
                      =& \sigma_X \sigma_Y \rho \frac{y - \mu_Y}{\sigma_Y^2} + \mu_X  \\
                      =& \frac{Cov(X,Y)(y - \mu_Y)}{Var[Y]} + \mathds{E}[X]  \\
                      =& \mathds{E}[X] + \frac{Cov(X,Y)(y - \mathds{E}[Y])}{Var[Y]}  \\
                      =& \mathds{E}[X] + \frac{Cov(X,Y)}{Var[Y]}(y - \mathds{E}[Y])  \quad \text{(Q.E.D)}  \\
  \end{aligned}
\end{equation}
  
In addition:  

\begin{equation}
  \begin{aligned}
    Var[X \Big| Y = y] =& Var \Big[ \sigma_X \rho \frac{y - \mu_Y}{\sigma_Y} + \sigma_X \sqrt{1 - \rho^2}Z_2 + \mu_X \Big| Y=y \Big]  \\
                       =& Var \Big[ \sigma_X \rho \frac{y - \mu_Y}{\sigma_Y} \Big| Y=y \Big ] + Var \Big[ \sigma_X \sqrt{1 - \rho^2}Z_2 \Big| Y=y \Big] + Var \Big[ \mu_X \Big| Y=y \Big]  \\
                       =& 0 + \sigma_X^2(1 - \rho^2) Var[Z_2] + 0  \\
                       =& \sigma_X^2(1 - \rho^2) * 1  \\
                       =& (1 - \rho^2)Var[X]  \quad \text{(Q.E.D)}  \\
  \end{aligned}
\end{equation}
  
  
# **Question 3**    

