---
title: "Homework 6"
author: "Jeff Nguyen"
date: "05/12/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, envir=.GlobalEnv)
```

**Pre-MFE Probability Seminar**  
**Baruch College, Fall 2020**  


Homework 06  
Student Name: Ngoc Son (Jeff) Nguyen  


# **Question 1**  

## a) Find the joint pdf $f_{X,Y}$  

We have the domain of $x$ and $y$ as follow:  
```{r}
curve(2-x/2, -1, 6, xlab="x", ylab="y", main="Domain")  # Plot x+2y=4
x_coord <- c(0,0,4)
y_coord <- c(0,2,0)
polygon(x_coord, y_coord, col="red")  # Shaded red polygon is the domain of x,y

# Adding lines to represent coordinates
abline(v=0)
abline(h=0)
```  
  
We can clearly see $x \in [0,4]$ and $y \in [0,2]$.  
When $x=0$ or $y=0$, $F(x,y) = 0$. Thus:

\begin{equation}
  \begin{aligned}
    F_{X,Y}(x,y) =& Cxy(x^2 + y) * 1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
    \text{thus, by definition of pdf:}  \\
    f_{X,Y}(x,y) =& \frac{\partial^2}{{\partial x} {\partial y}} F_{X,Y}(x,y) \\
                 =& \frac{\partial^2}{{\partial x} {\partial y}} Cxy(x^2 + y) * 
                    1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
                 =& \frac{\partial}{\partial x}\Big[ \frac{\partial (Cx^3y + Cxy^2)}{\partial y} \Big] * 
                    1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
                 =& \frac{\partial}{\partial x} (Cx^3 + 2Cxy) * 
                    1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
                 =& (3Cx^2 + 2Cy) * 1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
  \end{aligned}
\end{equation}
  
## b) Determine the constant $C$  

By definition, $\lim\limits_{(x,y) \to [4,2]} F_{X,Y}(x,y) = 1$. With this, we have:  

\begin{equation}
  \begin{aligned}
    F_{X,Y}(x,y) =& \int \int_{D} f_{X,Y}(x,y) \, dxdy   \\
                 =& \int_{0}^{2} \int_{0}^{4} (3Cx^2 + 2Cy) \, dxdy  \\
                 =& C \int_{0}^{2} \int_{0}^{4} (3x^2 + 2y) \, dxdy  \\
                 =& C \int_{0}^{2} \quad \int_{0}^{4} (3x^2 + 2y)dx \quad dy  \\
                 =& C \int_{0}^{2} \quad \Big( \frac{3x^4}{4} + 2yx \Big|_{x=0}^{x=4} \Big) \quad dy  \\
                 =& C \int_{0}^{2} (192 + 8y)dy  \\
                 =& C (192y + 4y^2) \Big|_{y=0}^{y=2}  \\
                 =& C(384 + 16)  \\
                 =& 400C \\
    \text{plug in:}  \\
    1 =& 400C \\
    C =& \frac{1}{400} \\
  \end{aligned}
\end{equation}
  
Thus the constant $C = \frac{1}{400}$.  

## c) Determine the marginal pdf $f_X$ and $f_Y$  

If $t \geqslant 0$:  

\begin{equation}
  \begin{aligned}
    F_X(t) =& P(X \leqslant t)   \\
           =& \int \int_{u \leqslant t} f_{X,Y}(u,v)dudv   \\
    f_{X,Y}(u,v) =& \frac{1}{400} (3u^2 + 2v) * 1_{\{ u \in [0,4], v \in [0,2]\}}(u,v)  \\
    D =& \{{u \leqslant t}\} \cap \{{u \in [0,4], v \in [0,2]}\}  \\
  \end{aligned}
\end{equation}  

We have the domain of $u$ and $v$ as follow:  
```{r}
curve(2-x/2, -1, 6, xlab="u", ylab="v", main="Domain")  # Plot x+2y=4
x_coord <- c(0,0,4)
y_coord <- c(0,2,0)
polygon(x_coord, y_coord, col="red")  # Shaded red polygon is the domain of x,y

# Adding lines to represent coordinates
abline(v=0)
abline(h=0)

abline(v=3)  # Adding line to represent t boundary

u_coord <- c(0,0,3,3)
v_coord <- c(0,2,.5,0)
polygon(u_coord, v_coord, col="green")  # Shaded green polygon is the domain of u,v
```
  
We have:  

\begin{equation}
  \begin{aligned}
    F_X(t) =& \int \int_{D} f_{X,Y}(u,v) \, dvdu   \\
           =& \int_{0}^{t} \int_{0}^2 f_{X,Y}(u,v) \, dvdu   \\
           =& \int_{0}^{t} \int_{0}^2 \frac{1}{400} (3u^2 + 2v) \, dvdu   \\
           =& \frac{1}{400} \int_{0}^{t} \quad \int_{0}^2 (3u^2 + 2v)dv \quad du   \\
           =& \frac{1}{400} \int_{0}^{t} (3u^2v + v^2) \Big|_{v=0}^{v=2} \quad du \\
           =& \frac{1}{400} \int_{0}^{t} (6u^2 + 4)du \\
           =& \frac{1}{400} (6u^2 + 4) \Big|_{u=0}^{u=t} \\
           =& \frac{1}{400} 6t^2 \\
           =& \frac{3t^2}{200}  \\
  \end{aligned}
\end{equation}
  
If $t<0$: $F_X(t) = P(X<0) = 0$. Thus: $F_X(t) = \frac{3t^2}{200} * 1_{[0,4]}(t)$.  

Therefore, by definition: $f_X(t) = F_X^{'}(t) = \frac{3t}{100} * 1_{[0,4]}(t)$.  

In addition:  

If $s \geqslant 0$:  

\begin{equation}
  \begin{aligned}
    F_Y(s) =& P(Y \leqslant s)   \\
           =& \int \int_{v \leqslant s} f_{X,Y}(u,v)dudv   \\
    f_{X,Y}(u,v) =& \frac{1}{400} (3u^2 + 2v) * 1_{\{ u \in [0,4], v \in [0,2]\}}(u,v)  \\
    G =& \{{v \leqslant s}\} \cap \{{u \in [0,4], v \in [0,2]}\}  \\
  \end{aligned}
\end{equation}  

We have the domain of $u$ and $v$ as follow:  
```{r}
curve(2-x/2, -1, 6, xlab="u", ylab="v", main="Domain")  # Plot x+2y=4
x_coord <- c(0,0,4)
y_coord <- c(0,2,0)
polygon(x_coord, y_coord, col="red")  # Shaded red polygon is the domain of x,y

# Adding lines to represent coordinates
abline(v=0)
abline(h=0)

abline(u=1.5)  # Adding line to represent s boundary

u_coord <- c(0,0,1,4)
v_coord <- c(0,1.5,1.5,0)
polygon(u_coord, v_coord, col="blue")  # Shaded blue polygon is the domain of u,v
```
  
We have:  

\begin{equation}
  \begin{aligned}
    F_Y(s) =& \int \int_{G} f_{X,Y}(u,v) \, dudv   \\
           =& \int_{0}^{s} \int_{0}^4 f_{X,Y}(u,v) \, dudv   \\
           =& \int_{0}^{s} \int_{0}^4 \frac{1}{400} (3u^2 + 2v) \, dudv   \\
           =& \frac{1}{400} \int_{0}^{s} \quad \int_{0}^2 (3u^2 + 2v)dv \quad dv   \\
           =& \frac{1}{400} \int_{0}^{s} (u^3 + 2uv) \Big|_{u=0}^{u=2} \quad dv \\
           =& \frac{1}{400} \int_{0}^{s} (64 + 8v)dv \\
           =& \frac{1}{400} (64v + 4v^2) \Big|_{v=0}^{v=s} \\
           =& \frac{1}{400} 64s + 4s^2 \\
           =& \frac{16s + s^2}{100}  \\
  \end{aligned}
\end{equation}
  
If $s<0$: $F_Y(s) = P(Y<0) = 0$. Thus: $F_X(t) = \frac{16s + s^2}{100} * 1_{[0,2]}(s)$.  

Therefore, by definition: $f_Y(s) = F_Y^{'}(s) = \frac{16s + s^2}{100} * 1_{[0,2]}(s)$.
  
## d) Determine the conditional pdf $f_{X|Y}$ and $f_{Y|X}$  

By definition:

\begin{equation}
  \begin{aligned}
    f_{X|Y}(x|y) =& \frac{f_{X,Y}(x,y)}{f_Y(y)}  \\
                 =& \frac{\frac{1}{400} (3x^2 + 2y) * 1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)}{\frac{16y + y^2}{100} * 1_{[0,2]}(s)}  \\
                 =& \frac{1}{4} * \frac{3x^2 + 2y}{16y + y^2}  \\
                 =& \frac{3x^2 + 2y}{64y + 4y^2}  \\
  \end{aligned}
\end{equation}
  
Also, by definition:

\begin{equation}
  \begin{aligned}
    f_{Y|X}(y|x) =& \frac{f_{X,Y}(x,y)}{f_X(x)}  \\
                 =& \frac{\frac{1}{400} (3x^2 + 2y) * 1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)}{\frac{3x}{100} * 1_{[0,4]}(x)}  \\
                 =& \frac{1}{4} * \frac{3x^2 + 2y}{3x}  \\
                 =& \frac{3x^2 + 2y}{12x}  \\
  \end{aligned}
\end{equation}
  
# **Question 2**
  
The pdf of $X$ where $X \sim N(\mu,\sigma^2)$ is given by $f_X(x) = \frac{1}{\sigma\sqrt{2\pi}}e^{\frac{-(x-\mu)^2}{2\sigma^2}}$.  

With $Y = e^{-X}$, we note that $supp(Y) = (0,\infty) \quad \forall \, y \in (0,\infty)$. By definition, the pdf of $Y$ is given by:  

\begin{equation}
  \begin{aligned}
    F_Y(y) =& P(Y \leqslant y)  \\
           =& P(e^{-X} \leqslant y)  \\
           =& P(X \geqslant -lny)  \\
           =& \int_{-lny}^{\infty} e^{\frac{-(x-\mu)^2}{2\sigma^2}}dx * 1_{(0,\infty)}(y) \\
           =& \Big[ \frac{1}{\sigma\sqrt{2\pi}} \int_{-lny}^{\infty} e^{\frac{-(x-\mu)^2}{2\sigma^2}}dx \Big] * 1_{(0,\infty)}(y)  \\
  \end{aligned}
\end{equation}
  
Hence, for any $y \in (0,\infty)$:  

\begin{equation}
  \begin{aligned}
    f_Y(y) =& F_Y^{'}(y)  \\
           =& \frac{d}{dy} \Big( \frac{1}{\sigma\sqrt{2\pi}} \int_{-lny}^{\infty} e^{\frac{-(x-\mu)^2}{2\sigma^2}} \Big) * 1_{(0,\infty)}(y)  \\
           =& \Big[ -\frac{1}{\sigma\sqrt{2\pi}} e^{\frac{-(lny-\mu)^2}{2\sigma^2}} \frac{d}{dy} (-lny) \Big] * 1_{(0,\infty)}(y)  \\
           =& \frac{1}{y\sigma\sqrt{2\pi}} e^{\frac{-(lny-\mu)^2}{2\sigma^2}} * 1_{(0,\infty)}(y)  \\
  \end{aligned}
\end{equation}
  
# **Question 3**
  
We are given $f_X(x) = 2x*1_{[0,1]}(x)$.  

In addition we have $Y|X \sim U(0,x)$. This gives the pdf of $Y|X$: $f_{Y|X}(y|x) = \frac{1}{x-0} * 1_{[0,x]}(y|x)$.  

Thus, by definition of conditional density:  

\begin{equation}
  \begin{aligned}
    f_{X,Y}(x,y) =& f_{Y|X}(y|x) * f_X(x)  \\
                 =& \frac{1}{x} * 1_{[0,x]}(y|x) * 2x * 1_{[0,1]}(x) \\
                 =& 2 * 1_{[0,x]}(y|x) * 1_{[0,1]}(x)
  \end{aligned}
\end{equation}

We can see that $supp(X) = [0,1]$ and $supp(Y) = [0,x]$.  

For any $y \in [0,1]$:  

\begin{equation}
  \begin{aligned}
    f_Y(y) =& \int_{D_y} f_{X,Y}(x,y)dx  \\
           =& \int_{y}^1 2dx  \\
           =& 2x \Big|_{x=y}^{x=1}  \\
           =& 2 - 2y \\
           =& 2(1 - y)  \\
  \end{aligned}
\end{equation}
  
For any $y \notin [0,1]$, the integrand's value is 0.

Therefore, $f_Y(y) = 2(1 - y) * 1_{[0,1]}(y)$.
  
# **Question 4**  

The pdf of $X$ where $X \sim U(0,1)$ is given by $f_X(x) = \frac{1}{1-0} * 1_{[0,1]}(x) = 1_{[0,1]}(x)$.  

With $Y = X^p \quad \forall \, p \neq 0$, we note that $supp(Y) = [0,1]$. By definition, the pdf of $Y$ is given by:  

\begin{equation}
  \begin{aligned}
    F_Y(y) =& P(Y \leqslant y)  \\
           =& P(X^p \leqslant y)  \\
  \end{aligned}
\end{equation}

For $p>0$:  

\begin{equation}
  \begin{aligned}
    F_Y(y) =& P(X \leqslant y^{\frac{1}{p}})  \\
           =& \int_{0}^{y^{\frac{1}{p}}} dx * 1_{[0,1]}(y)  \\
  \end{aligned}
\end{equation}
  
Hence, for any $y \in [0,1]$:  

\begin{equation}
  \begin{aligned}
    f_Y(y) =& F_Y^{'}(y)  \\
           =& \frac{d}{dy} \Big( \int_{0}^{y^{\frac{1}{p}}} dx \Big) * 1_{[0,1]}(y)  \\
           =& x \Big|_{x=0}^{x=y^{\frac{1}{p}}} * 1_{[0,1]}(y)  \\
           =& y^{\frac{1}{p}} * 1_{[0,1]}(y)
  \end{aligned}
\end{equation}
  
For $p<0$:  

\begin{equation}
  \begin{aligned}
    F_Y(y) =& P(X \geqslant y^{\frac{1}{p}})  \\
           =& \int_{y^{\frac{1}{p}}}^{1} dx * 1_{[0,1]}(y)  \\
  \end{aligned}
\end{equation}
  
Hence, for any $y \in [0,1]$:  

\begin{equation}
  \begin{aligned}
    f_Y(y) =& F_Y^{'}(y)  \\
           =& \frac{d}{dy} \Big( \int_{y^{\frac{1}{p}}}^{1} dx \Big) * 1_{[0,1]}(y)  \\
           =& x \Big|_{x=y^{\frac{1}{p}}}^{x=1} * 1_{[0,1]}(y)  \\
           =& \big( 1 - y^{\frac{1}{p}} \big) * 1_{[0,1]}(y)
  \end{aligned}
\end{equation}
  
# **Question 5**  

By definition, $X$ and $Y$ to have the standard bivariate normal distribution with correlation $p$ if their joint pdf is given by:  

\begin{equation}
  \begin{aligned}
    f_{XY}(x,y) =& \frac{1}{2\pi\sqrt{1-p^2}} e^{-\frac{1}{2(1-p^2)} (x^2 - 2pxy + y^2)}  \\
    \text{at} \quad p =& \frac{1}{2}\text{:}  \\
    f_{XY}(x,y) =& \frac{1}{2\pi\sqrt{1-\frac{1}{2}^2}} e^{-\frac{1}{2\Big(1-\frac{1}{2}^2\Big)} \Big(x^2 - 2\frac{1}{2}xy + y^2\Big)}  \\
                =& \frac{1}{\pi\sqrt{3}} e^{-\frac{2}{3} (x^2 - xy + y^2)}  \\
  \end{aligned}
\end{equation}
  
Thus, by definition:  

\begin{equation}
  \begin{aligned}
    P(X \geqslant 0, Y \geqslant 0) =& \int_{0}^{\infty} \int_{0}^{\infty} \frac{1}{\pi\sqrt{3}} e^{-\frac{2}{3} (x^2 - xy + y^2)} dydx  \\
                                    =& \int_{0}^{\infty} \frac{1}{\pi\sqrt{3}} \int_{0}^{\infty} e^{-\frac{2}{3} \Big(\frac{x^2}{4} - xy + y^2 + \frac{3x^2}{4} \Big)} dy \quad dx  \\
                                    =& \int_{0}^{\infty} \frac{1}{\pi\sqrt{3}} \int_{0}^{\infty} e^{-\frac{2}{3} \Big(\frac{x}{2} - y\Big)^2 -\frac{2}{3} \Big(\frac{3x^2}{4} \Big)} dy \quad dx  \\
                                    =& \int_{0}^{\infty} \frac{1}{\pi\sqrt{3}} \int_{0}^{\infty} e^{-\frac{2}{3} \Big(\frac{x}{2} - y\Big)^2} * e^{-\frac{2}{3} \Big(\frac{3x^2}{4} \Big)} dy \quad dx  \\
                                    =& \int_{0}^{\infty} \frac{1}{\pi\sqrt{3}} \int_{0}^{\infty} e^{-\frac{2}{3} \Big(\frac{x}{2} - y\Big)^2} * e^{\Big(\frac{-x^2}{2} \Big)} dy \quad dx  \\
                                    =& \int_{0}^{\infty} \frac{e^{\Big(-\frac{x^2}{2} \Big)}}{\pi\sqrt{3}} \int_{0}^{\infty} e^{-\frac{2}{3} \Big(\frac{x}{2} - y\Big)^2} dy \quad dx  \\
    \text{Transform variable:} z =& \frac{x}{2} - y  \\
    P(X \geqslant 0, Y \geqslant 0) =& \int_{0}^{\infty} \frac{e^{\Big(-\frac{x^2}{2} \Big)}}{\pi\sqrt{3}} \int_{-\infty}^{x^2} -e^{-\frac{2}{3}z^2} dz \quad dx  \\
                                    =& \int_{0}^{\infty} \frac{e^{\Big(-\frac{x^2}{2} \Big)}}{\pi\sqrt{3}} * \Big(-\frac{\pi}{\sqrt{3}} \Big) \quad dx  \\
                                    =& -\int_{0}^{\infty} \frac{e^{\Big(-\frac{x^2}{2} \Big)}}{3} dx  \\
                                    =& \frac{1}{3}
  \end{aligned}
\end{equation}