---
title: "Homework6"
author: "Jeff Nguyen"
date: "05/12/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, envir=.GlobalEnv)
```

**Pre-MFE Probability Seminar**  
**Baruch College, Fall 2020**  


Homework 06  
Student Name: Ngoc Son (Jeff) Nguyen  


# **Question 1**  

## a) Find the joint pdf $f_{X,Y}$  

We have the domain of $x$ and $y$ as follow:  
```{r}
curve(2-x/2, -1, 6, xlab="x", ylab="y", main="Domain")
x_coord <- c(0,0,4)
y_coord <- c(0,2,0)
polygon(x_coord, y_coord, col="red")
abline(v=0)
abline(h=0)
```  
  
We can clearly see $x \in [0,4]$ and $y \in [0,2]$.  
When $x=0$ or $y=0$, $F(x,y) = 0$. Thus:

\begin{equation}
  \begin{aligned}
    F_{X,Y}(x,y) =& Cxy(x^2 + y) * 1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
    \text{thus, by definition of pdf:}  \\
    f_{X,Y}(x,y) =& \frac{\partial^2}{{\partial x} {\partial y}} F_{X,Y}(x,y) \\
                 =& \frac{\partial^2}{{\partial x} {\partial y}} Cxy(x^2 + y) * 
                    1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
                 =& \frac{\partial}{\partial x}\Big[ \frac{\partial (Cx^3y + Cxy^2)}{\partial y} \Big] * 
                    1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
                 =& \frac{\partial}{\partial x} (Cx^3 + 2Cxy) * 
                    1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
                 =& (3Cx^2 + 2Cy) * 1_{\{ x \in [0,4], y \in [0,2]\}}(x,y)  \\
  \end{aligned}
\end{equation}
  
# b) Determine the constant $C$  

By definition, $\lim\limits_{(x,y) \to [4,2]} F_{X,Y}(x,y) = 1$. With this, we have:  

\begin{equation}
  \begin{aligned}
    F_{X,Y}(x,y) =& \int \int_{D} f_{X,Y}(x,y) \, dxdy   \\
                 =& \int_{0}^{2} \int_{0}^{4} (3Cx^2 + 2Cy) \, dxdy  \\
                 =& C \int_{0}^{2} \int_{0}^{4} (3x^2 + 2y) \, dxdy  \\
                 =& C \int_{0}^{2} \quad \int_{0}^{4} (3x^2 + 2y)dx \quad dy  \\
                 =& C \int_{0}^{2} \quad \Big( \frac{3x^4}{4} + 2yx \Big|_{x=0}^{x=4} \Big) \quad dy  \\
                 =& C \int_{0}^{2} (192 + 8y)dy  \\
                 =& C (192y + 4y^2) \Big|_{y=0}^{y=2}  \\
                 =& C(384 + 16)  \\
                 =& 400C \\
    \text{plug in:}  \\
    1 =& 400C \\
    C =& \frac{1}{400} \\
  \end{aligned}
\end{equation}
  
Thus the constant $C=400$.